Append_smoothed_results

### 2016-11-17 Code/append_smoothed_results.Rmd

```{r load_datasets}
load(file = "/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/Sep6_BWgap.Rdata")
ktm_smoothed <- read.csv("/Users/corinneriddell/Dropbox/BlackWhiteGap/smoothed_results.csv")
```

>>>>

```{r load_datasets}
load(file = "/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/Sep6_BWgap.Rdata")
ktm_smoothed <- read.csv("/Users/corinneriddell/Dropbox/BlackWhiteGap/smoothed_results.csv")

ktm_rest_males <- read.csv("/Users/corinneriddell/Dropbox/BlackWhiteGap/males_restofstates6COD.csv")
ktm_rest_females <- read.csv("/Users/corinneriddell/Dropbox/BlackWhiteGap/females_restofstates6COD.csv")

```
